\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Bibliografia}

\bibitem{ecintro1}
    Leonard Charlap, David Robbins.
    \emph{An Elementary Introduction to Elliptic Curves}.
    CRD Expository Report 31, 1988.

\bibitem{ecintro2}
    Leonard Charlap, Raymond Coley.
    \emph{An Elementary Introduction to Elliptic Curves II}.
    CCR Expository Report 34, 1990.

\bibitem{silverman}
    Joseph Silverman.
    \emph{The Arithmetic of Elliptic Curves}.
    Springer-Verlag, 1994.

\bibitem{tsfasmanvladutnogin}
    Michael Tsfasman, Serge  Vl\v{a}du\c{t}, Dmitry Nogin.
    \emph{Algebraic Geometry Codes}.
    American Mathematical Society, 2007.

\bibitem{miller}
    Victor Miller.
    \emph{Short Programs for Functions on Curves}.
    IBM, 1986.

\bibitem{menezesokamotovanstone}
    Alfred Menezes, Tatsuaki Okamoto, Scott Vanstone.
    \emph{Reducing Elliptic Curve Logarithms in a Finite Field}.
    IEEE Transactions on Information Theory, 1993.

\bibitem{bonehfranklin}
    Dan Boneh, Matthew Franklin.
    \emph{Identity-based Encryption from the Weil Pairing}.
    Advances in Cryptology -- CRYPTO 2001, 2001.

\bibitem{yi}
    Xun Yi.
    \emph{An Identity-Based Signature Scheme from the Weil Pairing}.
    IEEE, 2003.

\bibitem{baggamolvacrosta}
    Walid Bagga, Refik Molva, Stefano Crosta.
    \emph{Policy-based Encryption Schemes from Bilinear Pairings}.
    ASIACSS'06, 2006.

\bibitem{fujisakiokamoto}
    Eiichiro Fujisaki, Tatsuaki Okamoto.
    \emph{Secure integration of asymmetric and symmetric encryption schemes}.
    Advances in Cryptology -- CRYPTO '99, 1999.

\bibitem{maurer}
    Ueli Maurer.
    \emph{Towards the Equivalence of Breaking the Diffie-Hellman Protocol
        and Computing Discrete Logarithms}.
    Advances in Cryptology -- CRYPTO '94, 1994.

\bibitem{schoof}
    René Schoof.
    \emph{Counting Points on Elliptic Curves over Finite Fields}.
    Journal de Théorie des Nombres de Bordeaux, 1995.

\bibitem{adlemanmandersmiller}
    Leonard Adleman, Kenneth Manders, Gary Miller.
    \emph{On Taking Roots in Finite Field}.
    18th Annual Symposium on Foundations of Computer Science, 1977.

\bibitem{rabin}
    Michael Rabin.
    \emph{Probabilistic Algorithms in Finite Fields}.
    SIAM Journal on Computing, 1980.

\bibitem{koblitz}
    Neal Koblitz.
    \emph{Elliptic Curve Cryptosystems}.
    American Mathematical Society, 1987.

\bibitem{rivestshamiradleman}
    Ronald Rivest, Adi Shamir, Leonard Adleman.
    \emph{A Method for Obtaining Digital Signatures
        and Public-Key Cryptosystems}.
    Communications of the ACM, 1978.

\bibitem{diffiehellman}
    Whitfield Diffie, Martin Hellman.
    \emph{New Directions in Cryptography}.
    IEEE Transactions on Information Theory, 1976.

\bibitem{clrs}
    Thomas Cormen, Charles Leiserson, Ronald Rivest, Clifford Stein.
    \emph{Wprowadzenie do algorytmów}.
    Wydawnictwa Naukowo-Techniczne, 2005.

\bibitem{python}
    Guido van Rossum et al.
    \emph{Python Programming Language}.
    \url{http://www.python.org/}, 1990-2011.

\bibitem{rfc}
    Steve Crocker, Steve Carr, Jeff Rulifson et al.
    \emph{Requests for Comments}.
    \url{http://tools.ietf.org/rfc/}, 1969-2011.

\bibitem{sage}
    William Stein et al.
    \emph{Sage}.
    \url{http://sagemath.org/}, 2005-2011.

\end{thebibliography}
